An Efficient Calculus for Generalised Parikh Images of Regular Languages

### 2022-07-07 main.tex
Fix dependency parse issue
Image descriptions, reference fixes

\begin{figure}[t]
  \centering
  \raisebox{5ex}{\includegraphics[scale=0.9]{counter_automaton_pre}}
  \hfill
  \includegraphics[scale=0.9]{counter_automaton}
  \caption{An automaton recognising the language $\mathtt{(ab|c)*}$
    (left), and a Parikh automaton describing the pre-image of this
    language under the substring operation~$\cdot[n:m]$ (right). For
    sake of presentation, the Parikh automaton contains
    $\epsilon$-transitions, which could be eliminated in the standard
    way.}\label{fig:parikh-automata}
    \end{figure}

@@

\begin{lstlisting}[caption={An example input file for \Catra{} for the problem introduced in \cref{sec:introduction:motivation}, illustrating every major syntax element. From beginning to end: synchronised (product) automata using the keyword \texttt{synchronised} (automata A and B), labels (except those with ranges), register increments, and constraints on the final values of their counters.}, label=lst:input-example]
  // So far we only support integer counters. Note that we have individual
  // counters for each automaton to avoid surprises for product construction.
  counter int l_a, l_b, l_c, r_c;

>>>>

\begin{figure}[t]
  \centering
  \raisebox{5ex}{
    \includegraphics[scale=0.9]{counter_automaton_pre}
    }
  \hfill
  \includegraphics[scale=0.9]{counter_automaton}
  \caption{An automaton recognising the language $\mathtt{(ab|c)*}$
    (left), and a Parikh automaton describing the pre-image of this
    language under the substring operation~$\cdot[n:m]$ (right). For
    sake of presentation, the Parikh automaton contains
    $\epsilon$-transitions, which could be eliminated in the standard
    way.}\label{fig:parikh-automata}
    \Description[An 2-state automaton (left) and a slightly larger automaton with counters (right).]{
      The rightmost automaton is the starts with an initial state with a self-loop on any character that increments both registers by one, followed by an epsilon transition to a state with a self-loop on c that increments the lower register by one. From that state, the automaton has an epsilon-transition into the accepting state, as well as a transition on a into a state with only a transition back again, both incrementing the lower register by one. The accepting state has a self-loop on any character that does nothing to the registers.
      }
    \end{figure}

@@

\begin{lstlisting}[caption={An example input file for \Catra{} for the problem introduced in \cref{sec:motivation}, illustrating every major syntax element. From beginning to end: synchronised (product) automata using the keyword \texttt{synchronised} (automata A and B), labels (except those with ranges), register increments, and constraints on the final values of their counters.}, label=lst:input-example]
  // So far we only support integer counters. Note that we have individual
  // counters for each automaton to avoid surprises for product construction.
  counter int l_a, l_b, l_c, r_c;
